\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-17 paper/main.tex
minor edits to additional functionalities section

\subsubsection{Additional functionality}

% Present the major functionalities of the software.

@@

%The \texttt{smuggle} keyword can be enabled and disabled at will by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above). When \texttt{davos} is imported, it is automatically activated by default. Activating \texttt{davos} triggers two things:
%\begin{enumerate}
%    \item The \texttt{smuggle()} function is injected into the IPython user namespace
%    \item The \texttt{davos} parser is registered as a custom IPython input transformer
%\end{enumerate}

The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above). When \texttt{davos} is first imported, it is activated automatically. Activating \texttt{davos} triggers two things: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer. IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code. The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function. For example, if a user runs a notebook cell containing
\begin{verbatim}
smuggle numpy as np    # pip: numpy>1.16,<=1.20 -vv,
\end{verbatim}
the code that is actually executed by the Python interpreter would be
\begin{verbatim}
smuggle(name="numpy", as_="np", installer="pip", args_str="""numpy>1.16,<=1.20 -vv""", installer_kwargs={`editable': False, `spec': `numpy>1.16,<=1.20', `verbosity': 2}).
\end{verbatim}
Because the \texttt{smuggle()} function is defined in the notebook namespace in order for this to work, it is also possible (though never necessary) to call it directly. Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless it has been overwritten and no longer refers to the \texttt{smuggle()} function, as well as deregister the \texttt{davos} parser from the set of input transformers that are run when each notebook cell is executed. While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.

>>>>

\subsubsection{Additional functionality}
% - js functions
% - complex use cases

@@

The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above). When \texttt{davos} is first imported, it is activated automatically. Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer. IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code. The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function. For example, if a user runs a notebook cell containing
\begin{verbatim}
smuggle numpy as np    # pip: numpy>1.16,<=1.20 -vv,
\end{verbatim}
the code that is actually executed by the Python interpreter would be
\begin{verbatim}
smuggle(name="numpy", as_="np", installer="pip", args_str="""numpy>1.16,<=1.20 -vv""", installer_kwargs={`editable': False, `spec': `numpy>1.16,<=1.20', `verbosity': 2}).
\end{verbatim}
Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly. Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless its value has been overwritten and no longer refers to the \texttt{smuggle()} function. It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed. While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.
